Draft

### 2017-02-28 Draft/draft.tex
New notes in Draft, about a specific function.
Minor updates to physicist-taper.sty. Adding some pitfalls to math in Draft.
[minor] Calculate Stirling's formula using saddle point method.

\usepackage{float}  % For H in figures
\usepackage{amsmath, amssymb} % For math
\usepackage{bbm} % for numbers with mathbb
\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
									% See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
\usepackage{graphicx}   % need for figures
\usepackage{cite} % For bibligraphy
\usepackage{fancyref} % For lazy reference \fref
\usepackage[unicode]{hyperref} % For hyperlink everything.
\usepackage{CJKutf8} % For Chinese characters
%\usepackage{ dsfont } % For double struck fonts
\usepackage{braket} 
\usepackage[T1]{fontenc}
\usepackage{listings}

\usepackage{amsthm}
\newtheorem{defi}{Definition}[section]
\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{prop}{Proposition}[section]
\newtheorem{coro}{Corollary}[section]
\theoremstyle{definition}
\newtheorem{ex}{Example}[section]

\usepackage{tensor}  % For tensor indices
\usepackage[all]{xy} % For drawing category diagrams
\usepackage{mathrsfs}

@@

\section{Anchor}
% This is just an anchor for seperating thebibliography from above contents.
\begin{thebibliography}{1}
	\bibitem{Sakurai} Sakurai, J. J. Modern Quantum Mechanics, Addison Wesley.
	\bibitem{BSCS} 
        Bosonization and Strongly Correlated Systems. Cambridge.
        \href{http://www.cambridge.org/us/academic/subjects/physics/condensed-matter-physics-nanoscience-and-mesoscopic-physics/bosonization-and-strongly-correlated-systems}{Cambridge Press Link}

    \bibitem{DETA} Martin Braun. Differential Equations and Their
    Applications. 4ed. Springer.
    \bibitem{Kardar} M. Kardar. Statistical Physics of Particles (2007)
    \bibitem{griffiths-EM} Introduction to Electrodynamics, 3rd,
    Griffiths
\end{thebibliography}
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.

>>>>

% For drawing category diagrams
% TODO: Clear the place where I used this obsolete XY-pic package
\usepackage[all]{xy}

% My own physics package
% The following line load the package xparse with additional option to
% prevent the annoying warnings, which are caused by the package
% "physics" loaded in package "physics-taper".
\usepackage[log-declarations=false]{xparse}
\usepackage{physicist-taper}

@@

\section{Anchor}
% This is just an anchor for seperating thebibliography from above contents.
\bibliographystyle{alphaurl}
\bibliography{cite}

\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.

### 2017-02-28 Draft/sections/misc-math.tex
[minor] Some Corrrections of typo.
[minor] Calculate Stirling's formula using saddle point method.

$\triangle \cdot 2 = \triangle$, What will be of $\triangle + 1$?
\subsection{Funcation satisfying \texorpdfstring{$f(x+y)=f(x)f(x)$}{}}
\label{sec:Funcation satisfying \texorpdfstring{$f(x+y)=f(x)f(x)$}{}}

@@

\subsection{Matrix Operations}
    \subsubsection{Matrix Exponentials}
    \label{sec:Matrix-Exponentials}
    I found these formulae from Wikipedia page:
    \href{https://en.wikipedia.org/wiki/Baker%E2%80%93Campbell%E2%80%93Hausdorff_formula}{Baker–Campbell–Hausdorff formula}.
    \paragraph{The Zassenhaus formula}
    \begin{align}
        e^{t(X+Y)} &= e^{tX}~ e^{tY} ~e^{-\frac{t^2}{2} [X,Y]} ~
        e^{\frac{t^3}{6}(2[Y,[X,Y]]+ [X,[X,Y]] )} \nonumber\\
        & \times
          e^{\frac{-t^4}{24}([[[X,Y],X],X] + 3[[[X,Y],X],Y] + 3[[[X,Y],Y],Y]) }
        \times\cdots
    \end{align}

>>>>

$\triangle \cdot 2 = \triangle$, What will be of $\triangle + 1$?

\subsection{Gamma Function and Stirling's formula with Stationary phase
approximation/Saddle point approximation}

The Gamma Function for $z\in\C$ with a positive real part is

\begin{equation}
    \Gamma(z+1) = \int_0^\infty \dd{x} x^z e^{-x}
\end{equation}

It has an approximation formula called the Stirling formula. Here I obtain the
Stirling formula with the Saddle point approximation, also called Stationary
phase approximation in pp.108 of \cite{Altland2010}.

Let us further restrict $z$ into $z\in\R$ and $z>0$, the natural logarithm $\ln(z)$ is well
defined, so we have

\begin{equation}
    \int_0^\infty \dd{x} x^z e^{-x} = 
    \int_0^\infty \dd{x} e^{\ln(x^z)} e^{-x} = 
    \int_0^\infty \dd{x} e^{\ln(x^z)-x} 
\end{equation}

Let $F(x,z) = -(\ln(x^z)-x)$, then $\frac{dF}{dx}(x_0)=-\frac{z}{x_0}+1=0$ gives the
saddle point $x_0=z$. And $\frac{\dd[2]{F}}{\dd x^2}(x_0)=z/x_0^2=1/z>0$
confirms that this is really a minimum point. Therefore, the integration is
largely determined by the value around point $x_0=z$. Expanding $F$ around
$x_0=z$, we have
\begin{equation}
    F(x_0 + y)\approx F(x_0=z) + \frac{1}{2z} y^2 
    = z-\ln(z^z) + \frac{1}{2z}y^2
\end{equation}
Therefore
\begin{align}
    \int_0^\infty \dd{x} e^{\ln(x^z)-x} &= 
    \int_0^\infty \dd{x} e^{-F(x,z)} \approx
    \int_{-z}^\infty \dd{y} e^{-z+\ln(z^z) - \frac{1}{2z}y^2}
\end{align}

Now as $z\to\infty$, we have
\begin{align}
    \int_0^\infty \dd{x} e^{\ln(x^z)-x}
    &\approx e^{-z+\ln(z^z)} \int_{-\infty}^\infty \dd{y} e^{- \frac{1}{2z}y^2} 
    = e^{z(\ln(z)-1)} \sqrt{2\pi z} \nonumber\\
    &= e^{\ln(z^z)}e^{-z}\sqrt{2\pi z}
    = (\frac{z}{e})^z \sqrt{2\pi z}
\end{align}
Thus we have
\begin{equation}
    \Gamma(z+1) \overset{z\to\infty}{\approx} e^{z(\ln(z)-1)} \sqrt{2\pi z}
    = (\frac{z}{e})^z \sqrt{2\pi z}
\end{equation}
\subsection{Funcation satisfying \texorpdfstring{$f(x+y)=f(x)f(x)$}{}}
\label{sec:Funcation satisfying \texorpdfstring{$f(x+y)=f(x)f(x)$}{}}

@@

\subsection{Matrix Operations}
    \subsubsection{Matrix Exponentials}
    \label{sec:Matrix-Exponentials}
    \paragraph{The Zassenhaus formula}
    I found the formula from Wikipedia page:
    \href{https://en.wikipedia.org/wiki/Baker%E2%80%93Campbell%E2%80%93Hausdorff_formula}{Baker–Campbell–Hausdorff formula}.
    \begin{align}
        e^{t(X+Y)} &= e^{tX}~ e^{tY} ~e^{-\frac{t^2}{2} [X,Y]} ~
        e^{\frac{t^3}{6}(2[Y,[X,Y]]+ [X,[X,Y]] )} \nonumber\\
        & \times
          e^{\frac{-t^4}{24}([[[X,Y],X],X] + 3[[[X,Y],X],Y] + 3[[[X,Y],Y],Y]) }
        \times\cdots
    \end{align}
